Case Study: 16S microbiome data (ENIGMA)

### 2018-07-06 datasets/microbiome/microbiome-enigma.Rmd
Remove NA pvalues in microbiome-enigma Al

```{r, al-pvals}
if (!file.exists(al_result_file)) {
    res <- test_microbiome_corr(abundance = abun_otu, meta_col = meta$Al_mgL,
                                shift = zeroabun)
    saveRDS(res, file = al_result_file)
} else {
    res <- readRDS(al_result_file)
}
```

>>>>

```{r, al-pvals}
if (!file.exists(al_result_file)) {
    res <- test_microbiome_corr(abundance = abun_otu, meta_col = meta$Al_mgL,
                                shift = zeroabun)
    saveRDS(res, file = al_result_file)
} else {
    res <- readRDS(al_result_file)
}

# remove OTUs with missing pvals
res <- res %>% filter(!is.na(pval))
```
